Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-02-19 supplementary_material.tex
Updates from Overleaf

This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_su} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, and Sumatra.
Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/easter.pdf}
  \caption{\small{PSF test for Easter Island.
  A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.  A 75~km diameter positive Gaussian anomaly is placed at a depth of 150~km beneath Yellowstone.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.}}
  \label{fig:psf_easter}
\end{figure}

@@

In addition to section~7.1, we provide more detailed comparisons with GLAD-M15. Fig.~\ref{fig:m15_hotspot} shows the comparisons of $V_{sv}$ perturbations in the plumes and Fig.~\ref{fig:m15_subduction} shows comparisons n the subduction areas. In both figures, GLAD-M25 shows enhancements and emerging features compared to GLAD-M15.

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figures/compare_M15/hotspot.pdf}
  \caption{\small{Vertical cross sections for various plumes and hotspots for model GLAD-M15($V_\textrm{sv}$, left column) and GLAD-M25($V_\textrm{sv}$; right column).
  The map in the middle shows the cross section with color-coded red, green, and white dots for geographical reference; hotspots are denoted by red triangles.
  The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1000~km.
  (a) Afar; (b) Canary (left) and Hoggar (right); (c) Easter (left) and Galapagos (right); (d) Samoa; (e) Tahiti (middle) and Macdonald (right); (f) Iceland.
  }}
  \label{fig:m15_hotspot}
\end{figure}

>>>>

This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, ,Sumatra and two extra locations in United States..
Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/easter.pdf}
  \caption{\small{PSF test for Easter Island.
  A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.}}
  \label{fig:psf_easter}
\end{figure}

@@

In addition to Section~7.1 in the main text, here we provide more detailed comparisons with GLAD-M15~\citep{bozdaug2016global}. Fig.~\ref{fig:m15_hotspot} shows comparisons of $V_{sv}$ perturbations in for plumes, and Fig.~\ref{fig:m15_subduction} shows comparisons in subduction areas. In both figures, GLAD-M25 shows enhancements and emerging features relative to GLAD-M15.

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figures/compare_M15/hotspot.pdf}
  \caption{\small{Vertical cross sections for various plumes and hotspots for model GLAD-M15 ($V_\textrm{sv}$, left column) and GLAD-M25 ($V_\textrm{sv}$; right column).
  The map in the middle shows the cross section with color-coded red, green, and white dots for geographical reference; hotspots are denoted by red triangles.
  The dashed black semicircles in the cross sections denote depths of 410~km, 660~km, and 1,000~km.
  (a) Afar; (b) Canary (left) and Hoggar (right); (c) Easter (left) and Galapagos (right); (d) Samoa; (e) Tahiti (middle) and Macdonald (right); (f) Iceland.
  }}
  \label{fig:m15_hotspot}
\end{figure}
